A Detailed Demographic Analysis of 2020 U.S. Presidential Election Through Multilevel Regression and Post-Stratification

### 2024-03-20 paper/paper.qmd
updated README, abstract and introduction

---
title: "A Detailed Demographic Analysis of 2020 U.S. Presidential Election Through Multilevel Regression and Post-Stratification"
subtitle: "The Impact of Gender, Educatoin, Geographic location on Voter Preferences"
author: 
  - Jeongwoo Kim
  - Jiwon Choi
thanks: "Code and data are available at: https://github.com/Kjeongwoo99/2020_US_Election_Result_Analysis"
date: today
date-format: long
abstract: "In this study, we analyzed the 2020 U.S. Presidential Election outcomes using a sophisticated statistical technique called multilevel regression with post-stratification (MRP), applied to a large-scale national survey dataset and census data. Our findings reveal how demographic factors such as gender, education, and geographic location influence voting behavior, with particular emphasis on voter preferences for Donald Trump. The analysis highlights significant variations in voter support across gender, states and educational backgrounds and how they shape electoral outcomes. This research contributes to our understanding of the American electoral landscape, demonstrating the critical role of demographic diversity in determining the direction of political preferences and election results."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

The paper begins by introducing the broader context and motivation behind our study. It then discusses the specifics of the data sources and the variables that we considered important. This is followed by the presentation of the data and a discussion of our findings regarding education, gender, and state in voter preference.

@@

# Model
For our study, we employ a technique called multilevel regression with post-stratification (MRP). This approach involves creating a model based on a smaller data set, such as our survey data, and then extending the model's findings to a larger population.

@@

# Results

@@

# Discussion

>>>>

---
title: "A Detailed Demographic Analysis of 2020 U.S. Presidential Election Through Multilevel Regression and Post-Stratification"
subtitle: "The Impact of Gender, Educatoin, Geographic location on Voter Preferences"
author: 
  - Jeongwoo Kim
  - Jiwon Choi
thanks: "Code and data are available at: https://github.com/Kjeongwoo99/2020_US_Election_Result_Analysis"
date: today
date-format: long
abstract: "In this study, we analyzed the 2020 U.S. Presidential Election outcomes using multilevel regression with post-stratification (MRP), applied to a large-scale national survey dataset and census data. Our findings reveal how demographic factors such as gender, education, and geographic location influence voting behavior, with particular emphasis on voter preferences for Donald Trump. The analysis highlights significant variations in voter support across gender, states and educational backgrounds and how they shape electoral outcomes. This research contributes to our understanding of the American electoral landscape, demonstrating the critical role of demographic diversity in determining the direction of political preferences and election results."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

The paper begins by introducing the broader context and motivation behind our study. @sec-data then discusses specifics of the data sources and the variables that we considered important. @sec-model introduces the specifics of the logistic regression model with post-stratification methods. This is followed by the presentation of the data in @sec-results and discussions of our findings regarding education, gender, and state in voter preference in @sec-discussion.

@@

# Model {#sec-model}
For our study, we employ a technique called multilevel regression with post-stratification (MRP). This approach involves creating a model based on a smaller data set, such as our survey data, and then extending the model's findings to a larger population.

@@

# Results {#sec-results}

@@

# Discussion {#sec-discussion}
